Include a header paragraph specific to your product here. Safety requirements might address items specific to your product such as: no exposure to toxic chemicals; lack of sharp edges that could harm a user; no breakable glass in the enclosure; no direct eye exposure to infrared/laser beams; packaging/grounding of electrical connections to avoid shock; etc.

This section will provide brief explanation on safety requirement while using this product. There are various risk factors included while operating the Brewing system. Since we are dealing with electrical appliances, there is always a risk of getting electrocuted if proper attention is not given. 

\subsection{Safety Hazards while Working with the Electricity}
\subsubsection{Description}
Different electrical appliances like electric heater will be used in this project alongside with water. Even a small misplaced or leakage of water into the micro controller can damage it and can put the user in electrical hazards. While working with mash, it is important to note how hot the mash is in order to prevent burn.

\subsubsection{Source}
A basic safety measure taken while working with any electrical appliances, especially when a liquid is nearby.

\subsubsection{Constraints}
The product must be built closed to a place where there is electrical plugs. Once built, the product can be difficult and time-consuming to move. The user should be present at the site while brewing at first for some batches to make sure everything is running smoothly.

\subsubsection{Standards}
Non-applicable.

\subsubsection{Priority}
Top-priority should be given as this is concerned with the health of the user.


\subsection{Kill switch}
\subsubsection{Description}
The system must provide a hardware kill switch as well as an option on the touch screen interface to activate the kill switch. Once activated, the system must immediately cut power to all pumps and heating elements.

\subsubsection{Source}
Sponsor

\subsubsection{Constraints}
N/A

\subsubsection{Standards}
N/A

\subsubsection{Priority}
Critical
